\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final Proxi}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation; the contributions prior to Rev0 are
NOT included.

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 3\\
Ajay Grewal & 3\\
Savinay Chhabra & 3\\
Amanbeer Singh Minhas & 3\\
Gourob Podder & 3\\
\bottomrule
\end{tabular}
\end{table}


\section{Supervisor/Stakeholder Meeting Attendance}


\noindent \textbf{Supervisor's Name: } This project has no supervisor \\
\noindent \textbf{Stakeholders: } Seniors, Students and Working professionals

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 8\\
Ajay Grewal & 1\\
Savinay Chhabra & 1\\
Amanbeer Singh Minhas & 5\\
Gouroub Podder & 1\\
\bottomrule
\end{tabular}
\end{table}

Individual Team Members had chats with their grandparents and asked them questions
about their experiences during with their computing devices. Amanbeer met with various
seniors and working professionals to get their feedback on the Proxi. These chats were
used to generate a usability report and were informal and not scheduled meetings.



\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 0\\
Ajay Grewal & 0\\
Savinay Chhabra & 0\\
Amanbeer Singh Minhas & 0\\
Gourob Podder & 0\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}


\noindent \textbf{TA's Name: } Christopher Schankula

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Ajay Grewal & 1\\
Savinay Chhabra & 1\\
Amanbeer Singh Minhas & 1\\
Gouroub Podder & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 56 & 100\% \\
Ajay Grewal & 3 & 5.4\% \\
Savinay Chhabra & 19 & 33.9\% \\
Amanbeer Singh Minhas & 4 & 7.1\% \\
Gouroub Podder & 30 & 53.6\% \\
\bottomrule
\end{tabular}
\end{table}

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Ajay Grewal & 2 & 1 \\
Savinay Chhabra & 3 & 1 \\
Amanbeer Singh Minhas & 3 & 1 \\
Gourob Podder & 3 & 2 \\
\bottomrule
\end{tabular}
\end{table}

\section{Team Charter Trigger Items}

\textbf{Trigger Summary:} Based on our team charter, the primary triggers
for intervention include:
\begin{itemize}
  \item Missing a scheduled team or supervisor meeting without at least
        24 hours notice.
  \item Repeated missed deadlines or uncommunicated delays on assigned
        deliverables (more than 1--2 occurrences).
  \item Consistently arriving late to meetings without prior notice.
  \item Submitting low-quality or incomplete work without explanation.
  \item Disruptive behavior or conflict without attempting resolution
        through team discussion.
\end{itemize}

\noindent\textbf{Observed Trigger Events:} No formal trigger violations occurred
during this period. All absences or delays were communicated in advance and
approved by the team. Examples include:
\begin{itemize}
  \item One member joined virtually for the TA meeting as they were sick.
\end{itemize}

All instances were communicated promptly and did not affect project progress
or deliverable quality.

\vspace{0.5em}
\noindent\textbf{Plan and Reflection:} No corrective actions were necessary as all
team members demonstrated responsibility and respect for deadlines and
communication. Moving forward, the team will:
\begin{itemize}
  \item Continue to provide early notice of scheduling conflicts.
  \item Balance academic workload and project responsibilities fairly.
  \item Maintain consistent participation and accountability.
\end{itemize}

Our current triggers remain appropriate and effective, requiring no revisions
at this stage.

\section{Additional Productivity Metrics}

To measure our overall progress and teamwork, the following simple
metrics were tracked during the period leading up to the Final demo:

\begin{itemize}
  \item \textbf{Meeting participation:} Each member attended over 90\%
        of team and supervisor meetings.
  \item \textbf{On-time submissions:} All major deliverables were submitted 
        before the deadline.
  \item \textbf{Peer review response time:} Feedback on documents was
        usually provided within 2 days.
\end{itemize}

\end{document}