\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{float}
\usepackage{placeins}
\usepackage{longtable}
\usepackage{caption}

\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\input{../Comments}
\input{../Common}

\begin{document}

\title{System Verification and Validation Plan for \progname{}} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
30 October 2025 & 1.0 & Added V\&V plan.\\
8 March 2026 & 1.1 & Revised the V\&V plan to address TA feedback:
added introductory text for Section 1; corrected spelling, grammar, and
document flow issues; replaced magic numbers with symbolic constants where
appropriate; standardized terminology and stylization such as macOS; moved
table titles above tables and added in-text references to tables; added a
role reassignment plan for V\&V team members; refined review checklists so
items are atomic and directly checkable; clarified specific WCAG checks to
be used for accessibility verification; added tests for unintended and
unauthorized actions, including destructive and replay-style scenarios;
included draft checklists referenced by the plan; clarified traceability by
adding requirement-to-test matrix coverage; and made walkthroughs,
inspections, stakeholder reviews, and project-specific extras more explicit
and justified.\\
\bottomrule
\end{tabularx}

\newpage

\tableofcontents

\newpage

\pagenumbering{arabic}

\noindent This document outlines the Verification and Validation plan for Project
Proxi. It explains how our team plans to evaluate the system we are
building against its requirements. The plan describes what tests will be
run, how documents and designs will be reviewed and validated, and how
the evidence collected traces back to the original SRS document. The main
goal is to make sure Project Proxi is reliable, easy to use, and
genuinely helpful for the people who rely on it for accessibility and
productivity.

\section{General Information}

\subsection{Summary}
The aim of this document is to present the verification and validation
plan for Project Proxi. Project Proxi is an AI-powered desktop assistant
that allows its users to interact with their computer using voice and
text. The target users for Project Proxi include seniors, individuals
with disabilities, and power users who want a more accessible,
efficient, and convenient way to perform computer tasks.

\subsection{Objectives}
The main objective of the Verification and Validation (V\&V) plan is to
confirm that Project Proxi satisfies its stated functional and
non-functional requirements and fulfills its primary purpose of improving
computer accessibility and efficiency for seniors, individuals with
disabilities, and power users.

\noindent The principal objectives that this V\&V plan aims to meet are:
\begin{itemize}
  \item \textbf{Verify Functional Correctness:} Ensure that the features
  described in the SRS are implemented and behave as expected through
  unit, integration, and system-level testing.
  \item \textbf{Validate Usability and Accessibility:} Demonstrate that
  users within the target demographic can effectively operate the system
  using voice and text while meeting the relevant accessibility
  requirements, including WCAG 2.2 guidance for accessible user
  interfaces.
  \item \textbf{Assess Performance and Reliability:} Confirm that the
  application meets performance, stability, and error-handling goals as
  defined in the SRS document.
  \item \textbf{Hardware Compatibility Testing:} Meet verification goals
  on a variety of consumer hardware devices. Specialized or adaptive
  devices will not be included; only commercially available Windows and
  macOS computers.
\end{itemize}

Out-of-scope objectives include extensive long-term field usability
studies, comprehensive privacy compliance, and specialized hardware
testing. The project will assume that any external libraries have
already been verified by their respective development teams. These
exclusions are justified given the project's limited time, budget, and
academic context. Verification efforts are therefore directed toward
objectives that help meet core software requirements.

\subsection{Challenge Level and Extras}

This project does not include a designated challenge level, as its
primary focus is on the development and validation of a functional,
accessible, and user-friendly AI-powered desktop assistant. The project
scope aligns with the general expectations of the capstone course and
emphasizes reliability, usability, and compliance with accessibility
standards rather than advanced AI research or complex algorithmic
innovation.

\noindent This project includes the following approved extras:
\begin{itemize}
  \item \textbf{Demo Video:} A demo video will show how to install, set
  up, and use the software in realistic scenarios. This extra is
  important because Project Proxi is intended for seniors, individuals
  with disabilities, and power users with varying levels of technical
  proficiency. The video supports onboarding by showing the expected
  workflow, common commands, and important interactions in a format that
  is easier to follow than text alone.
  \item \textbf{Usability Report:} A usability report will be developed
  to assess the system's core objectives and requirements. It will
  summarize the results of testing as specified in the SRS document.
  This extra is important because usability and accessibility are
  central goals of Project Proxi, and the report will help identify
  issues that can be used to improve the system before final delivery.
\end{itemize}

\subsection{Relevant Documentation}

The following documentation is directly relevant to the verification and
validation activities for Project Proxi:
\begin{itemize}
  \item \textbf{Development Plan [\citet{DevPlan}]:} This document
  defines the overall project workflow, timelines, and milestones for
  the different phases of the project.
  \item \textbf{Problem Statement and Goals [\citet{ProbStatement}]:}
  This document defines the problems, goals, and stakeholders of the
  project.
  \item \textbf{Software Requirements Specification [\citet{SRS}]:}
  Describes the functional and non-functional requirements of the
  project.
  \item \textbf{Hazard Analysis [\citet{HazardAnalysis}]:} This
  document identifies any potential sources of harm or risk that may be
  associated with the project. Potential risks such as unauthorized
  access, misuse, or data breaches and their mitigation strategies are
  documented here.
  \item \textbf{Usability Report [\citet{UsabilityReport}]:} Includes
  results of user evaluation and beta testing during the validation
  stage. It summarizes key findings related to the system meeting its
  design and usability goals.
  \item \textbf{Demo Video [\citet{UserInstructionalVideo}]:} Demonstrates how to
  install, set up, and use the software. It provides a guided
  walkthrough of major workflows and examples to support users with
  varying technical proficiency.
\end{itemize}

\section{Plan}
This section outlines the strategy for Verification and Validation (V\&V)
across all phases of the Project Proxi lifecycle. The plan defines the roles
and responsibilities of the V\&V team and specifies structured approaches for
verifying the Software Requirements Specification (SRS), Design, and
Implementation, as well as the approach for Software Validation. This
systematic process increases confidence in the correctness, accessibility,
and reliability of the final system.

Verification ensures that the system is built correctly and meets its stated
requirements, while validation confirms that the right system has been built
for its intended users. Both static techniques (reviews, inspections, and
walkthroughs) and dynamic techniques (testing and user evaluations) are used.
All artifacts, results, and issues are tracked through GitHub for full
traceability between requirements, test cases, and evidence.

\subsection{Verification and Validation Team}

The Verification and Validation team for Project Proxi is the Proxi project
team itself. Since the team is small, all members contribute to V\&V
activities in addition to their development responsibilities. Table~
\ref{tab:vnv-team} summarizes the primary V\&V responsibilities assigned to
each team member.

All verification tasks and results are peer reviewed, documented, and
tracked in GitHub to maintain accountability and consistent quality
assurance.

\begin{table}[H]
\caption{Verification and Validation Team Roles}
\label{tab:vnv-team}
\centering
\begin{tabular}{|p{3cm}|p{3.5cm}|p{7.5cm}|}
\hline
\textbf{Name} & \textbf{Role} & \textbf{V\&V Responsibilities} \\
\hline
Savinay Chhabra & Team Lead / Project Manager &
Coordinates all V\&V activities, schedules document and design reviews,
ensures traceability matrices are complete, and validates plan
feasibility. \\
\hline
Amanbeer Singh Minhas & Verification Engineer / Documentation Lead &
Authors test specifications, manages accessibility validation
(WCAG~2.2), executes functional and non-functional tests, and maintains
V\&V evidence and metrics. \\
\hline
Gourob Podder & AI / Backend Developer &
Verifies the accuracy and latency of voice, text, and natural language
processing modules, conducts integration and performance tests, and
performs code inspections. \\
\hline
Ajay Singh Grewal & Front-End / Integration Engineer &
Implements automated UI tests, validates responsiveness and error
handling, and ensures cross-platform consistency and workflow
reliability. \\
\hline
\end{tabular}
\end{table}

\subsection{Role Reassignment and Contingency Plan}

If timelines, availability, or project risks change, V\&V
responsibilities will be rebalanced using the following procedure:
\begin{itemize}
  \item The Team Lead identifies blocked work items and proposes
  reassignment within one business day.
  \item At least one backup reviewer is maintained for each critical
  activity, including SRS review, design review, test execution, and
  evidence tracking.
  \item Reassignments are recorded in a GitHub issue labeled
  \texttt{vnv-role-change}, including the new owner, due date, and
  rationale.
  \item The traceability matrix and meeting notes are updated in the
  same sprint to reflect responsibility changes.
\end{itemize}

\subsection{SRS Verification}

The Software Requirements Specification (SRS) will be verified using a
structured review process involving internal checks, peer feedback, and
consistency checks. The goal is to confirm that all requirements are clear,
consistent, complete, and ready for design and testing.

\vspace{0.5em}
\noindent\textbf{Planned Verification Stages:}
\begin{itemize}
\item \textbf{Internal Team Review:}
  Each team member reviews assigned SRS sections to ensure requirements are
  clearly written, uniquely numbered, feasible, and testable. Feedback and
  questions are added as GitHub issues under the \texttt{SRS-review} tag for
  tracking.

\item \textbf{Peer Team Feedback:}
  Another project team will review the SRS to identify unclear, ambiguous,
  inconsistent, or missing requirements. Their comments will be discussed in
  a short review meeting, and agreed changes will be included in the next SRS
  revision.

\item \textbf{Consistency and Traceability Check:}
  Manual and automated checks will confirm that every requirement label
  (functional, non-functional, and constraint-related) appears in the
  traceability matrix and links to one or more planned verification
  activities in the V\&V Plan. Any missing, duplicate, or inconsistent
  identifiers will be flagged for correction.

\item \textbf{Team Validation Meeting:}
  After all updates, the team will meet to confirm that project goals such as
  accessibility, reliability, safety, and usability are fully captured in the
  SRS. The final version will then be approved as the baseline for design and
  testing.
\end{itemize}

\vspace{0.5em}
\noindent\textbf{SRS Review Checklist:}
\begin{itemize}
\item Each requirement has a unique identifier.
\item Each requirement uses clear and unambiguous language.
\item Each requirement states one verifiable idea.
\item Each requirement is feasible within project scope.
\item Each requirement is testable by inspection, analysis, or execution.
\item Each requirement is consistent with the problem statement and goals.
\item Each requirement is consistent with the hazard analysis.
\item Accessibility requirements refer to WCAG 2.2 where applicable.
\item Requirements for voice and text interaction are both represented.
\item Safety-related requirements include confirmation or mitigation steps.
\item Every requirement appears in the traceability matrix.
\end{itemize}

\subsection{Design Verification}

The design of Project Proxi will be verified through focused peer reviews,
walkthroughs, and checklists to confirm that the architecture, interfaces,
and data flows align with the approved SRS. Each review will help identify
inconsistencies or missing details before implementation begins.

\vspace{0.5em}
\noindent\textbf{Planned Verification Activities:}
\begin{itemize}
\item \textbf{Internal Design Review:}
  Team members will examine assigned modules to ensure the design is modular,
  consistent with SRS requirements, and feasible for implementation. Each
  reviewer will complete a checklist covering module responsibilities,
  interface definitions, traceability, and error handling.

\item \textbf{Cross-Team Design Review:}
  Another project team will review the design documents and provide feedback
  on readability, logic, completeness, and consistency. Their comments will
  be logged as GitHub issues tagged \texttt{Design-review} and resolved in
  the next revision.

\item \textbf{Walkthrough Meeting:}
  The team will conduct a collaborative walkthrough in which each member
  explains the purpose, inputs, outputs, and dependencies of their assigned
  subsystem. Meeting notes will record identified issues, action items, and
  owners.

\item \textbf{Traceability Check:}
  A traceability matrix will confirm that every major design component maps to
  at least one SRS requirement and that every SRS requirement is supported by
  one or more design elements. Any unmatched modules or requirements will be
  flagged for revision before coding starts.
\end{itemize}

\vspace{0.5em}
\noindent\textbf{Design Review Checklist Items:}
\begin{itemize}
\item Each module has a unique name and purpose.
\item Each module states its responsibilities.
\item Each module states its inputs.
\item Each module states its outputs.
\item Each interface identifies exchanged data clearly.
\item Each interface is consistent across connected modules.
\item Each data flow matches the described system behavior.
\item Each module includes error handling where needed.
\item Each module avoids overlapping responsibilities.
\item Accessibility-related design elements are identified explicitly.
\item Support for voice and text interaction is represented in the design.
\item Each major component traces to at least one SRS requirement.
\end{itemize}

\subsection{Verification and Validation Plan Verification}

The Verification and Validation (V\&V) Plan itself will also be verified to
ensure it is complete, consistent, and realistic. This review confirms that
the plan defines clear responsibilities, test coverage, and measurable
evidence of software quality.

\vspace{0.5em}
\noindent\textbf{Planned Verification Activities:}
\begin{itemize}
\item \textbf{Internal Review:}
  Team members will inspect the V\&V Plan for completeness, logical flow, and
  consistency with other project documents such as the SRS, MIS, MG, and
  Hazard Analysis. Issues will be logged on GitHub under the tag
  \texttt{VnV-review}.

\item \textbf{Peer Team Review:}
  A partner project team will review the plan to provide external feedback on
  clarity, organization, feasibility, and coverage. Comments will be
  discussed in a team meeting, and accepted suggestions will be incorporated
  into the next version.

\item \textbf{Cross-Document Consistency Check:}
  The team will confirm that all V\&V activities listed here are consistent
  with the SRS, MIS, MG, and Hazard Analysis and that requirement identifiers
  match across artifacts.

\item \textbf{Review Process Validation:}
  Small intentional edits, such as removing a trace link or altering a test
  identifier, will be introduced to confirm that the team's review process
  can detect inconsistencies. This activity validates the effectiveness of
  the review workflow.
\end{itemize}

\vspace{0.5em}
\noindent\textbf{V\&V Plan Review Checklist:}
\begin{itemize}
\item All cited documents are correct and consistent.
\item Roles and responsibilities match Table~\ref{tab:vnv-team}.
\item Each section states its purpose clearly.
\item Each planned activity identifies expected evidence.
\item Each requirement is traced to one or more verification activities.
\item Each test identifier is unique and used consistently.
\item Internal review steps are defined clearly.
\item Peer review steps are defined clearly.
\item The plan is feasible within the project timeline and tools.
\end{itemize}

\subsection{Implementation Verification}

The implementation of Project Proxi will be verified through a combination of
dynamic and static techniques to ensure the system performs correctly,
reliably, and according to its specified design. This section summarizes how
unit, integration, and system testing activities will be supported by
automated tools and structured reviews.

\vspace{0.5em}
\noindent\textbf{Dynamic Verification:}
\begin{itemize}
\item \textbf{Unit Testing:}
  Each software module will have dedicated unit tests as outlined in the unit
  testing plan. Tests will confirm correct outputs, data flow, state changes,
  and error handling for input processing, planning, execution, and UI
  modules. Coverage results will be monitored through automated reports to
  ensure that major functions are exercised.

\item \textbf{Integration and System Testing:}
  Combined module testing will validate interactions between the input
  pipeline, user interface, planning components, execution components, and
  backend services. These tests correspond directly to the functional and
  non-functional test cases listed in this document.

\item \textbf{Mutation Testing:}
  To evaluate the quality of the test suite, small artificial faults
  (mutants) will be introduced into the codebase. Existing unit and system
  tests will be rerun to confirm that they detect the injected faults. A high
  mutation score will increase confidence in the strength and completeness of
  the test suite.
\end{itemize}

\vspace{0.5em}
\noindent\textbf{Static Verification:}
\begin{itemize}
\item \textbf{Code Walkthroughs and Inspections:}
  Scheduled walkthrough meetings will allow each developer to explain their
  code and receive peer feedback on structure, readability, traceability,
  error handling, and consistency with the design. Review notes will be
  recorded, and any required fixes will be tracked through GitHub issues or
  pull request comments.

\item \textbf{Static Analysis Tools:}
  Linters and analyzers, such as ESLint, Pylint, or similar tools, will be
  used to detect common issues, unused variables, inconsistent style, and
  potential logic errors. Results will be documented as part of the
  verification evidence.

\item \textbf{Code Review via Pull Requests:}
  All implementation changes will go through GitHub pull requests with at
  least one reviewer. Reviewers will verify coding standards, style,
  alignment with design diagrams, and whether the change preserves intended
  behavior without introducing unintended actions.
\end{itemize}

\subsection{Automated Testing and Verification Tools}

Automated tools will be used throughout the implementation phase to support
testing, continuous integration, and quality assurance. These tools help
reduce manual effort, detect regressions early, and provide measurable
evidence of software reliability and maintainability.

\vspace{0.5em}
\noindent\textbf{Automated Testing Framework:}
\begin{itemize}
\item The project will use \texttt{pytest} for automated unit,
  integration, and scripted scenario tests. Each major module will have
  dedicated test files and fixtures to verify inputs, outputs, state
  changes, and edge cases.
\item Scripted scenario tests will simulate realistic user interactions by
  submitting selected voice and text commands, capturing system responses,
  and comparing them against expected results.
\item For repeatable testing, scenario tests will use a predefined command
  set maintained by the team. The full set of commands used for automated
  testing will be listed explicitly in the corresponding test cases or in an
  appendix, rather than described only as a sample count.
\end{itemize}

\vspace{0.5em}
\noindent\textbf{Continuous Integration and Delivery (CI/CD):}
\begin{itemize}
\item GitHub Actions will be configured to automatically run linting and
  automated tests whenever code is pushed or a pull request is opened.
  The pipeline will help detect regressions early and ensure that changes
  are reviewed against a consistent verification process before merge.
\end{itemize}

\vspace{0.5em}
\noindent\textbf{Static Analysis and Linters:}
\begin{itemize}
\item Static analysis tools such as \texttt{pylint} and \texttt{flake8}
  will be used to detect syntax errors, unused variables, inconsistent
  style, and maintainability issues. Results will be logged and tracked
  as part of the verification evidence.
\end{itemize}

\vspace{0.5em}
\noindent\textbf{Build and Automation Utilities:}
\begin{itemize}
\item The project will use \texttt{make} commands and supporting scripts
  to automate environment setup, dependency installation, linting, and
  test execution. This helps ensure consistent verification results
  across development machines and the CI/CD pipeline.
\end{itemize}

\subsection{Software Validation}

Software validation confirms that Project Proxi satisfies user needs and
performs as intended in realistic scenarios. The focus is on showing that
the system achieves its goals of accessibility, responsiveness, safety,
and ease of use for seniors, individuals with disabilities, and power
users.

\vspace{0.5em}
\noindent\textbf{Planned Validation Activities:}
\begin{itemize}
\item \textbf{User Testing Sessions:}
  A small group of peers and volunteers will perform task-based
  evaluations, such as launching applications, entering text, and
  managing files through voice and text interaction. Their feedback will
  be used to assess ease of learning, efficiency, accessibility, and
  overall satisfaction.

\item \textbf{Accessibility Validation:}
  Validation will confirm that the interface supports the accessibility
  goals defined in the SRS and aligns with relevant WCAG~2.2 guidance.
  The evaluation will consider items such as readable contrast, text
  scaling, visible feedback, caption or transcript support where
  applicable, and whether key tasks can be completed clearly through the
  supported interaction modes.

\item \textbf{Stakeholder Review Session:}
  The team will present the system in a demonstration that acts as a
  validation milestone. Feedback from course staff and classmates will
  be collected through short surveys and review notes and then used to
  improve the user experience.

\item \textbf{Automated Scenario Validation:}
  Scripted scenario tests will submit a predefined and fully enumerated
  set of commands to the system, record the observed outputs, and compare
  them with expected behavior. These tests will help validate recurring
  tasks, command interpretation accuracy, response consistency, and
  protection against unintended actions.

\item \textbf{External Data and Comparison:}
  Where appropriate, publicly available speech or language datasets may
  be used to compare command interpretation behavior against baseline
  expectations. This provides an additional reference point for judging
  consistency and robustness.
\end{itemize}


\section{System Tests}

Each test is specific and measurable, providing sufficient detail for
replication once the system is built. The tests are grouped into logical
areas covering input handling, natural language understanding, task
execution, feedback mechanisms, memory management, logging, and system
safety.

\subsection{Tests for Functional Requirements}

The following tests verify that each functional requirement defined in the
SRS has been properly implemented and behaves as intended. Each test
specifies the type of testing, initial system state, inputs, expected
results, and how the test will be performed.

\subsubsection{Input and Recognition Requirements}

\begin{enumerate}

\item \textbf{Test FUNC.R.1 -- Speech and Text Input Acceptance}

\textbf{Type:} Functional / Manual Testing

\textbf{Initial State:} System initialized and idle at the main
interface.

\textbf{Input/Condition:} Users provide the following 20 valid commands.
Commands 1--10 are entered by text, and commands 11--20 are spoken
through the microphone interface.

{\renewcommand{\labelenumii}{\arabic{enumii}.}
\begin{enumerate}
  \item Summarize my latest unread email.
  \item Draft an email to John about tomorrow's team meeting.
  \item Show my calendar events for tomorrow.
  \item Create a calendar event for Friday at 2 PM called Team Sync.
  \item Search the web for Hamilton weather and summarize the result.
  \item Search the web for nearby walk-in clinics.
  \item Make a Notion page called Drinking Water Tracker.
  \item Add ``Drink 8 glasses today'' to my Drinking Water Tracker page.
  \item Summarize the file named Capstone Notes.
  \item What can I say?
  \item Summarize my latest unread email.
  \item Draft an email to John about tomorrow's team meeting.
  \item Show my calendar events for tomorrow.
  \item Create a calendar event for Friday at 2 PM called Team Sync.
  \item Search the web for Hamilton weather and summarize the result.
  \item Search the web for nearby walk-in clinics.
  \item Make a Notion page called Drinking Water Tracker.
  \item Add ``Drink 8 glasses today'' to my Drinking Water Tracker page.
  \item Summarize the file named Capstone Notes.
  \item What can I say?
\end{enumerate}
}

\textbf{Output/Result:} The system correctly accepts and interprets at
least 19 of the 20 inputs, and each accepted input is converted into the
expected internal command representation and displayed result.

\textbf{How test will be performed:} Each input and resulting interpreted
command will be logged automatically. The test supervisor will compare
the interpreted result against the expected result for all 20 commands
and calculate the success rate. Any rejected, misinterpreted, or
malformed results will be recorded for analysis.

\textbf{Functional Requirements Covered:} FUNC.R.1

\item \textbf{Test FUNC.R.2 -- Speech-to-Text Accuracy}

\textbf{Type:} Functional / Automated Evaluation

\textbf{Initial State:} System with speech-to-text enabled and
configured in a controlled acoustic environment.

\textbf{Input/Condition:} The following 10 spoken commands are each
recorded from 5 speakers, for a total of 50 audio samples:

{\renewcommand{\labelenumii}{\arabic{enumii}.}
\begin{enumerate}
  \item Summarize my latest unread email.
  \item Draft an email to John about tomorrow's team meeting.
  \item Show my calendar events for tomorrow.
  \item Create a calendar event for Friday at 2 PM called Team Sync.
  \item Search the web for Hamilton weather and summarize the result.
  \item Search the web for nearby walk-in clinics.
  \item Make a Notion page called Drinking Water Tracker.
  \item Add ``Drink 8 glasses today'' to my Drinking Water Tracker page.
  \item Summarize the file named Capstone Notes.
  \item What can I say?
\end{enumerate}
}

\textbf{Output/Result:} The resulting transcriptions achieve at least
90\% word accuracy across the full sample set.

\textbf{How test will be performed:} The 50 audio samples will be batch
fed into the speech-to-text component. Output transcripts will be
compared against reference transcripts using a word error rate metric,
and the overall accuracy will be computed from the full set.

\textbf{Functional Requirements Covered:} FUNC.R.2

\end{enumerate}

\subsubsection{Intent Understanding and Task Execution}

\begin{enumerate}

\item \textbf{Test FUNC.R.3 -- Intent Recognition Accuracy}

\textbf{Type:} Functional / Automated Testing

\textbf{Initial State:} Natural language understanding component
initialized with the current intent parsing configuration.

\textbf{Input/Condition:} The system is given the following 10 command
variants for each of 10 supported intents, for a total of 100 labeled
inputs. The supported intents are: summarize email, draft email, show
calendar, create calendar event, browser search, summarize browser
result, create Notion page, update Notion page, summarize file, and show
help or examples.

\textbf{Output/Result:} At least 90 of the 100 inputs are assigned the
correct ground-truth intent.

\textbf{How test will be performed:} A test script will feed the labeled
inputs into the intent parser. Predicted intents will be logged and
compared against human-labeled references to compute intent-level
accuracy.

\textbf{Functional Requirements Covered:} FUNC.R.3

\item \textbf{Test FUNC.R.4 -- Task Planning and Execution Success Rate}

\textbf{Type:} Functional / Integration Testing

\textbf{Initial State:} System active with required tools, permissions,
and network connectivity available.

\textbf{Input/Condition:} The following 20 representative high-level
commands are executed sequentially:

{\renewcommand{\labelenumii}{\arabic{enumii}.}
\begin{enumerate}
  \item Summarize my latest unread email.
  \item Draft an email to Sarah about the capstone update.
  \item Draft an email to John saying I will join in 10 minutes.
  \item Show my calendar events for tomorrow.
  \item Create a calendar event for Friday at 2 PM called Team Sync.
  \item Move my Team Sync event to 3 PM.
  \item Search the web for Hamilton weather.
  \item Summarize the current browser result.
  \item Search the web for nearby pharmacies.
  \item Summarize the top result in two sentences.
  \item Make a Notion page called Drinking Water Tracker.
  \item Add ``Drink 8 glasses today'' to my Drinking Water Tracker page.
  \item Make a Notion page called Capstone Tasks.
  \item Add ``Finish V\&V plan'' to my Capstone Tasks page.
  \item Summarize the file named Capstone Notes.
  \item Read the first paragraph of Capstone Notes aloud.
  \item Show the summary again.
  \item What can I say?
  \item Undo the last action.
  \item Cancel the current action.
\end{enumerate}
}

\textbf{Output/Result:} At least 17 of the 20 commands are completed
successfully and produce the intended task outcome in the interface.

\textbf{How test will be performed:} Commands will be executed one at a
time. Testers will verify whether each displayed result, draft, summary,
or state change matches the intended user goal. Failures will be logged
along with their cause, such as planning failure, permission failure, or
execution failure.

\textbf{Functional Requirements Covered:} FUNC.R.4

\end{enumerate}

\subsubsection{Feedback and Responsiveness}

\begin{enumerate}

\item \textbf{Test FUNC.R.5 -- Response Feedback Timing}

\textbf{Type:} Functional / Manual Timing

\textbf{Initial State:} System ready to execute user commands.

\textbf{Input/Condition:} The following 10 tasks are executed:
summarize latest unread email, draft an email, show tomorrow's calendar,
create a calendar event, search the web for Hamilton weather, summarize
the current result, search for nearby pharmacies, make a Notion page,
summarize a file, and show help commands.

\textbf{Output/Result:} Each command generates visible or spoken
feedback within 2 seconds after task completion or after the system
determines that the task cannot be completed.

\textbf{How test will be performed:} A timer will start at the moment the
task finishes or the failure state is known. Feedback appearance time
will be recorded for each trial, and all observed times will be compared
against the 2-second threshold.

\textbf{Functional Requirements Covered:} FUNC.R.5

\end{enumerate}

\subsubsection{Contextual Memory and Logging}

\begin{enumerate}

\item \textbf{Test FUNC.R.6 -- Contextual Follow-Up Interpretation}

\textbf{Type:} Functional / Manual Sequence Testing

\textbf{Initial State:} System with active short-term conversational
memory.

\textbf{Input/Condition:} Testers execute the following 10 conversational
sequences:

{\renewcommand{\labelenumii}{\arabic{enumii}.}
\begin{enumerate}
  \item Summarize my latest unread email. Reply to it with thanks.
  \item Draft an email to John. Change the subject to Project Update.
  \item Show my calendar for tomorrow. Add office hours at 4 PM.
  \item Create a calendar event for Friday at 2 PM. Move it to 3 PM.
  \item Search the web for Hamilton weather. Summarize it.
  \item Search the web for nearby walk-in clinics. Open the first result
  and summarize it.
  \item Make a Notion page called Drinking Water Tracker. Add today's
  intake to it.
  \item Make a Notion page called Capstone Tasks. Add testing checklist
  to it.
  \item Summarize the file named Capstone Notes. Read it aloud.
  \item Show my latest drafted email. Send it.
\end{enumerate}
}

\textbf{Output/Result:} At least 9 of the 10 sequences are completed with
correct interpretation of follow-up references such as ``it'', ``that'',
or omitted repeated context.

\textbf{How test will be performed:} Each sequence will be entered by a
tester. The interpreted actions and resulting displayed outputs will be
reviewed to confirm that contextual references are resolved correctly.

\textbf{Functional Requirements Covered:} FUNC.R.6

\item \textbf{Test FUNC.R.7 -- Interaction and Task Logging Verification}

\textbf{Type:} Functional / Inspection

\textbf{Initial State:} Logging module enabled with write access to the
configured storage location.

\textbf{Input/Condition:} The following 10 sessions are performed, with a
mix of successful and failed tasks using both voice and text:
summarize email, draft email, create calendar event, make Notion page,
browser search, file summary, invalid command, send draft then cancel,
browser request with network disabled, and undo last action.

\textbf{Output/Result:} Each session generates a timestamped log entry
containing the received input, interpreted intent, resulting action, and
final outcome.

\textbf{How test will be performed:} After each session, reviewers will
inspect the recorded logs for completeness, correct timestamps, session
identifiers, action summaries, and outcome fields.

\textbf{Functional Requirements Covered:} FUNC.R.7

\end{enumerate}

\subsubsection{Usability and Safety}

\begin{enumerate}

\item \textbf{Test FUNC.R.8 -- High-Level Command Usability}

\textbf{Type:} Usability / Observational Testing

\textbf{Initial State:} Deployed system interface with voice and text
interaction enabled.

\textbf{Input/Condition:} 10 participants attempt the following 10 core
tasks using Proxi's high-level interface: summarize an unread email,
draft an email, show tomorrow's calendar, create a calendar event,
search the web, summarize a browser result, make a Notion page, update a
Notion page, summarize a file, and use the help command.

\textbf{Output/Result:} At least 80\% of attempted tasks are completed
successfully without requiring users to interact with low-level system
details such as raw file paths, terminal commands, or manual system
configuration steps.

\textbf{How test will be performed:} Observers will record whether each
task is completed successfully, whether low-level system details were
needed, and where users hesitated or failed. Completion rate will be
computed over the full task set across all participants.

\textbf{Functional Requirements Covered:} FUNC.R.8

\item \textbf{Test FUNC.R.9 -- Privileged Action Confirmation}

\textbf{Type:} Functional / Safety Validation

\textbf{Initial State:} System running with permission-sensitive actions
enabled.

\textbf{Input/Condition:} The following privileged commands are issued by
both voice and text: send the drafted email, delete an email draft,
delete a calendar event, remove a Notion page, and clear saved session
history. For each command, one trial confirms the action and one trial
cancels the action.

\textbf{Output/Result:} Every privileged command triggers a confirmation
prompt before execution. Confirmed actions execute only after explicit
approval, and cancelled actions do not execute.

\textbf{How test will be performed:} Testers will issue each privileged
command twice, once followed by confirmation and once followed by
cancel. Observers will verify that the prompt appears before execution
and that the final result matches the approval or cancellation path.

\textbf{Functional Requirements Covered:} FUNC.R.9

\end{enumerate}


\subsection{Tests for Non-Functional Requirements}

This section defines specific tests used to determine whether Proxi meets
its non-functional requirements. Each test is derived from the SRS and
states how the result will be verified.

\subsubsection{Look and Feel Requirements}

\begin{enumerate}

\item \textbf{Test NF.LF.1 -- UI Conformance and Readability}

\textbf{Type:} Static Inspection / Manual Testing

\textbf{Initial State:} Latest UI build available in the chat-style
frontend.

\textbf{Input/Condition:} Review the main screens, transcript area,
status indicators, and primary controls using the following checklist:
listen control visible, stop or cancel control visible, undo control
visible, status indicators readable, transcript area readable, minimal
visual clutter, advanced options hidden from the default flow, large
click targets, and theme toggle present.

\textbf{Output/Result:} All checklist items are present and usable in the
main workflow.

\textbf{How test will be performed:} Two reviewers will inspect the UI
independently, complete the checklist, compare results, and record any
issues with screenshots.

\textbf{Non-Functional Requirements Covered:} APP.1, APP.2, APP.3,
APP.4, APP.5

\item \textbf{Test NF.LF.2 -- Style and Iconography Check}

\textbf{Type:} Static Inspection / Manual Testing

\textbf{Initial State:} Build with spoken output, on-screen text, and
the final icon set enabled.

\textbf{Input/Condition:} Trigger the following outputs and review the
resulting labels, captions, and icons:
welcome message, task success message, task failure message,
confirmation prompt, cancel action, undo action, help response, and one
browser summary response.

\textbf{Output/Result:} Labels are short and plain, spoken output also
appears on screen, and icons are consistent and paired with short text
labels.

\textbf{How test will be performed:} Reviewers will inspect the
displayed strings and visual elements, then record any inconsistencies
with screenshots or screen recordings.

\textbf{Non-Functional Requirements Covered:} STY.1, STY.2, STY.3

\end{enumerate}

\subsubsection{Usability and Humanity Requirements}

\begin{enumerate}

\item \textbf{Test NF.US.1 -- Task-Based Usability and Learnability}
\textbf{Study}

\textbf{Type:} Dynamic / Manual Usability Testing

\textbf{Initial State:} New users receive a 5-minute orientation to
Proxi.

\textbf{Input/Condition:} Each participant performs the following 10
core tasks:
summarize an unread email, draft an email, show tomorrow's calendar,
create a calendar event, search the web, summarize a browser result,
make a Notion page, update a Notion page, summarize a file, and use the
``What can I say?'' help feature.

\textbf{Output/Result:} Main actions are discoverable, most everyday
tasks are completed without assistance after the orientation, repeated
tasks become faster, example commands are easy to find, messages are
clear, risky actions are confirmed, and error messages suggest a next
step.

\textbf{How test will be performed:} Observers will measure task
completion, task time, repeated-task improvement, and requests for help.
Participants will also complete a short survey on clarity and ease of
use.

\textbf{Non-Functional Requirements Covered:} EOU.R.1, EOU.R.2,
EOU.R.3, LEA.R.1, LEA.R.2, UAP.R.1, UAP.R.2, UAP.R.3

\item \textbf{Test NF.US.2 -- Accessibility, Personalization, and}
\textbf{Locale}

\textbf{Type:} Dynamic Testing / Accessibility Inspection

\textbf{Initial State:} Build with voice and text enabled; captions,
scalable text, and contrast-compliant themes implemented.

\textbf{Input/Condition:} Execute the following voice-only tasks:
start setup, ask for help, summarize an unread email, show tomorrow's
calendar, create a calendar event, cancel the current action, undo the
last action, and exit the app. Then inspect the interface for the
following accessibility checks: captions shown for spoken responses,
text resizes to 200\% without loss of information, and color contrast
meets WCAG~2.2 guidance for readable text. Also verify that date, time,
and language outputs follow Canadian English formatting.

\textbf{Output/Result:} All listed tasks can be completed through the
voice-only path, captions are present for spoken responses, text scaling
works without loss of function, contrast is sufficient, and Canadian
English formats are used consistently.

\textbf{How test will be performed:} Reviewers will run the voice-only
task suite, inspect captions and scaled layouts, check contrast using an
accessibility checker, and verify locale-formatted outputs in the
interface.

\textbf{Non-Functional Requirements Covered:} ACC.R.1, ACC.R.2,
PER.R.1, PER.R.2

\end{enumerate}

\subsubsection{Performance and Reliability Requirements}

\begin{enumerate}

\item \textbf{Test NF.PF.1 -- Latency and Recognition Accuracy Study}

\textbf{Type:} Dynamic / Automated Performance Testing

\textbf{Initial State:} Standard hardware environment with typical
system load.

\textbf{Input/Condition:} Run the following 10 commands in a quiet room
and then repeat the same 10 commands in a moderately noisy indoor
environment:
summarize an unread email, draft an email, show tomorrow's calendar,
create a calendar event, search the web for Hamilton weather, summarize
the browser result, search for nearby pharmacies, make a Notion page,
summarize a file, and use the help command.

\textbf{Output/Result:} Voice responses begin within the SAL.R.1 limit,
common actions complete within the SAL.R.2 limit, quiet-environment
recognition accuracy meets POA.R.1, and moderate-noise accuracy meets
POA.R.2.

\textbf{How test will be performed:} The team will time each command,
compare recognized inputs against expected inputs, compute command
accuracy for both environments, and record the results in a test log.

\textbf{Non-Functional Requirements Covered:} SAL.R.1, SAL.R.2,
POA.R.1, POA.R.2

\item \textbf{Test NF.PF.2 -- Robustness and Capacity Study}

\textbf{Type:} Dynamic / Automated and Manual Testing

\textbf{Initial State:} System running on standard hardware.

\textbf{Input/Condition:} Submit the following invalid or adverse
inputs:
empty command, incomplete command, unsupported command, malformed text
input, interrupted speech input, network-dependent request with network
disabled, and a cancelled action. Then run the system continuously for
at least 4 hours under normal usage.

\textbf{Output/Result:} Input errors are logged and reported without a
crash, the system continues running after invalid or incomplete
commands, continuous operation is maintained for at least 4 hours, and
CPU usage stays within the CAP.R.2 limit during normal operation.

\textbf{How test will be performed:} Reviewers will trigger each listed
failure condition, inspect logs and on-screen errors, monitor whether
the system remains usable, and record runtime and CPU usage during the
continuous run.

\textbf{Non-Functional Requirements Covered:} ROFT.R.1, ROFT.R.2,
CAP.R.1, CAP.R.2

\item \textbf{Test NF.PF.3 -- Safety, Extensibility, and Longevity}
\textbf{Study}

\textbf{Type:} Dynamic / Manual and Checklist-Based Testing

\textbf{Initial State:} System running with undo support, update
support, and MCP tool registry enabled.

\textbf{Input/Condition:} Perform the following actions:
delete a draft and cancel, delete a draft and confirm, remove a
calendar event and undo it, add one new MCP tool through the registry,
update the build, and simulate an update rollback.

\textbf{Output/Result:} Destructive actions require confirmation,
critical actions can be undone in one step, a new feature becomes
available without major changes to existing functionality, user settings
persist after update, and rollback completes within the LON.R.2 limit.

\textbf{How test will be performed:} Reviewers will execute the listed
actions, verify confirmation and undo behavior, register one new MCP
tool, confirm that it loads correctly, update the system, and then
measure the rollback process.

\textbf{Non-Functional Requirements Covered:} SAF.R.1, SAF.R.2,
SOE.R.1, SOE.R.2, LON.R.1, LON.R.2

\end{enumerate}

\subsubsection{Operational and Environmental Requirements}

\begin{enumerate}

\item \textbf{Test NF.OP.1 -- Environment and Ecosystem Fit}

\textbf{Type:} Dynamic / Checklist-Based Testing

\textbf{Initial State:} Fresh install on current Windows and macOS
systems with required integrations enabled.

\textbf{Input/Condition:} Run the system indoors under normal operating
conditions, including moderate indoor noise, user distance within
approximately one meter of the microphone, and room temperature between
15$^\circ$C and 30$^\circ$C. Perform a browser search, email task, file
summary task, and calendar task while other common desktop applications
are also running.

\textbf{Output/Result:} The system operates effectively within the
expected physical environment, speech recognition remains usable within
the specified distance and indoor noise conditions, and automation does
not interfere with other running applications.

\textbf{How test will be performed:} Reviewers will execute the listed
tasks under the specified conditions, note any environmental failures,
and check whether other applications continue to function normally.

\textbf{Non-Functional Requirements Covered:} EPE.R.1, EPE.R.2,
EPE.R.3, EPE.R.4, WER.R.1, WER.R.2

\item \textbf{Test NF.OP.2 -- Interfaces, Packaging, and Release Check}

\textbf{Type:} Dynamic / Inspection and Checklist Testing

\textbf{Initial State:} Release candidate build, release notes, and
deployment package available.

\textbf{Input/Condition:} Perform a clean install, verify external
integrations with email, browser, file, and speech services, inspect
communication protocol use, inspect external interaction logs, and
review the packaged release.

\textbf{Output/Result:} Interfaces with adjacent systems use the
expected protocols and logging, the product installs with minimal setup,
the release follows the versioning scheme, and the release package is
version controlled and archived.

\textbf{How test will be performed:} Reviewers will perform a clean
install, execute one task per integration, inspect logs for external
interactions, and review release artifacts, tags, and packaged files.

\textbf{Non-Functional Requirements Covered:} IAS.R.1, IAS.R.2,
IAS.R.3, IAS.R.4, PRD.R.1, PRD.R.2, PRD.R.3, REL.R.1, REL.R.2

\end{enumerate}

\subsubsection{Maintainability and Support Requirements}

\begin{enumerate}

\item \textbf{Test NF.MS.1 -- Onboarding, Support, and Adaptability}

\textbf{Type:} Dynamic / Checklist-Based Testing

\textbf{Initial State:} Fresh clone of the repository, README present,
Report Problem feature present, and configuration file editable.

\textbf{Input/Condition:} A new contributor follows the README to build
and run the project, adds one new MCP tool using a module and registry
entry, generates a support bundle through Report Problem, and changes
the default app configuration without changing code.

\textbf{Output/Result:} The build and run process succeeds without help,
a new MCP tool is added without modifying existing tools, the support
bundle contains recent logs and basic system information with consent,
and the system continues working after only a configuration change.

\textbf{How test will be performed:} The team will time the setup,
verify that the new contributor can complete the README steps, add and
register one tool, inspect the generated ZIP bundle, modify the default
app configuration, and rerun the affected task flow.

\textbf{Non-Functional Requirements Covered:} 14.1-1, 14.1-2, 14.2-1,
14.2-2, 14.3-1, 14.3-2

\end{enumerate}

\subsubsection{Security Requirements}

\begin{enumerate}

\item \textbf{Test NF.SEC.1 -- Access, Integrity, Privacy, and}
\textbf{Immunity}

\textbf{Type:} Dynamic / Inspection and Security Scanning

\textbf{Initial State:} Fresh install, privacy policy available, and
dependency scanner configured.

\textbf{Input/Condition:} Verify that no account is required to use the
app, trigger actions that require explicit permission, inspect stored
and transmitted data for protection and minimization, review user
consent steps for third-party services, and run dependency
vulnerability scans.

\textbf{Output/Result:} No registration is required, required
permissions must be explicitly granted by the user, stored or
transmitted data is protected from unauthorized alteration, stored data
handling aligns with PIPEDA expectations, third-party data sharing is
minimized and consented to, and no known dependency vulnerabilities
remain unresolved at release time.

\textbf{How test will be performed:} Reviewers will execute permission
flows, inspect privacy-related behavior and consent prompts, inspect
logs and network traffic at a high level, and run software composition
and dependency scans.

\textbf{Non-Functional Requirements Covered:} ACS-01, ACS-02, INT-01,
PRIV-01, IMM-01, IMM-02

\item \textbf{Test NF.SEC.2 -- Replay or Unauthorized Voice Command}

\textbf{Type:} Dynamic / Manual Security Testing

\textbf{Initial State:} System running with voice input enabled.

\textbf{Input/Condition:} Play a recorded high-risk voice command, or
have a different person issue a destructive command such as deleting a
draft or removing an event.

\textbf{Output/Result:} The system does not execute the action silently.
It must either reject the command, require explicit confirmation, or log
the event for review.

\textbf{How test will be performed:} Reviewers will issue a risky
command using a recording and then using a second speaker, and will
verify that the action is not completed without the expected safeguard.

\textbf{Non-Functional Requirements Covered:} SAF.R.1, ACS-02

\end{enumerate}

\subsubsection{Cultural Requirements}

\begin{enumerate}

\item \textbf{Test NF.CUL.1 -- Language and Tone Check}

\textbf{Type:} Static Inspection / Manual Testing

\textbf{Initial State:} Final strings, prompts, and language settings
available.

\textbf{Input/Condition:} Review common screens and messages, including
welcome text, help text, error messages, confirmation prompts, task
success messages, and cancellation messages. Then switch languages and
repeat a subset of basic flows.

\textbf{Output/Result:} Wording remains polite and culturally neutral,
avoids slang and confusing references, and multiple languages support
the basic interaction flow.

\textbf{How test will be performed:} Two reviewers will inspect the
default language strings, then one reviewer will switch languages,
repeat the selected flows, and record any broken or untranslated text.

\textbf{Non-Functional Requirements Covered:} CULR-01, CULR-02

\end{enumerate}

\subsubsection{Compliance Requirements}

\begin{enumerate}

\item \textbf{Test NF.COM.1 -- Legal and Standards Compliance Check}

\textbf{Type:} Static Inspection / Checklist Testing

\textbf{Initial State:} License file, privacy policy, accessibility
notes, and release artifacts available in the repository.

\textbf{Input/Condition:} Review legal and standards compliance against
the following checklist:
PIPEDA handling for stored user data, MIT license presence and wording,
WCAG~2.2 accessibility evidence, and documentation of software quality
and security practices aligned with ISO~25010 and ISO~27001 goals.

\textbf{Output/Result:} Required legal notices are present, the release
uses the MIT license correctly, privacy documentation aligns with stated
behavior, and standards-compliance evidence is present and consistent
with the implementation.

\textbf{How test will be performed:} Reviewers will inspect policies,
license files, release notes, and accessibility evidence, then record
any missing or inconsistent items in a compliance checklist.

\textbf{Non-Functional Requirements Covered:} LGL-01, LGL-02,
STDCOMP-01, STDCOMP-02

\end{enumerate}

\subsection{Traceability Between Test Cases and Requirements}
\label{section:5.3}

Tables~\ref{tab:fr-trace}, \ref{tab:nfr-trace-a}, and
\ref{tab:nfr-trace-b} show that every requirement defined in the SRS
is covered by at least one planned system test.

\begin{table}[H]
\centering
\small
\caption{Functional Requirements Traceability Matrix}
\label{tab:fr-trace}
\begin{tabularx}{\textwidth}{|c|*{9}{>{\centering\arraybackslash}X|}}
\hline
Test ID & F1 & F2 & F3 & F4 & F5 & F6 & F7 & F8 & F9 \\
\hline
FUNC.R.1 & $\times$ & & & & & & & & \\
\hline
FUNC.R.2 & & $\times$ & & & & & & & \\
\hline
FUNC.R.3 & & & $\times$ & & & & & & \\
\hline
FUNC.R.4 & & & & $\times$ & & & & & \\
\hline
FUNC.R.5 & & & & & $\times$ & & & & \\
\hline
FUNC.R.6 & & & & & & $\times$ & & & \\
\hline
FUNC.R.7 & & & & & & & $\times$ & & \\
\hline
FUNC.R.8 & & & & & & & & $\times$ & \\
\hline
FUNC.R.9 & & & & & & & & & $\times$ \\
\hline
\end{tabularx}
\end{table}
\FloatBarrier

\noindent
Functional requirement keys:
F1 = FUNC.R.1, F2 = FUNC.R.2, F3 = FUNC.R.3, F4 = FUNC.R.4,
F5 = FUNC.R.5, F6 = FUNC.R.6, F7 = FUNC.R.7, F8 = FUNC.R.8,
F9 = FUNC.R.9.

\begin{table}[H]
\centering
\small
\caption{Non-Functional Requirements Traceability Matrix Part 1}
\label{tab:nfr-trace-a}
\begin{tabularx}{\textwidth}{|c|*{6}{>{\centering\arraybackslash}X|}}
\hline
Req ID & LF1 & LF2 & US1 & US2 & PF1 & PF2 \\
\hline
APP.1 & $\times$ & & & & & \\
\hline
APP.2 & $\times$ & & & & & \\
\hline
APP.3 & $\times$ & & & & & \\
\hline
APP.4 & $\times$ & & & & & \\
\hline
APP.5 & $\times$ & & & & & \\
\hline
STY.1 & & $\times$ & & & & \\
\hline
STY.2 & & $\times$ & & & & \\
\hline
STY.3 & & $\times$ & & & & \\
\hline
EOU.R.1 & & & $\times$ & & & \\
\hline
EOU.R.2 & & & $\times$ & & & \\
\hline
EOU.R.3 & & & $\times$ & & & \\
\hline
LEA.R.1 & & & $\times$ & & & \\
\hline
LEA.R.2 & & & $\times$ & & & \\
\hline
UAP.R.1 & & & $\times$ & & & \\
\hline
UAP.R.2 & & & $\times$ & & & \\
\hline
UAP.R.3 & & & $\times$ & & & \\
\hline
ACC.R.1 & & & & $\times$ & & \\
\hline
ACC.R.2 & & & & $\times$ & & \\
\hline
PER.R.1 & & & & $\times$ & & \\
\hline
PER.R.2 & & & & $\times$ & & \\
\hline
SAL.R.1 & & & & & $\times$ & \\
\hline
SAL.R.2 & & & & & $\times$ & \\
\hline
POA.R.1 & & & & & $\times$ & \\
\hline
POA.R.2 & & & & & $\times$ & \\
\hline
ROFT.R.1 & & & & & & $\times$ \\
\hline
ROFT.R.2 & & & & & & $\times$ \\
\hline
CAP.R.1 & & & & & & $\times$ \\
\hline
CAP.R.2 & & & & & & $\times$ \\
\hline
\end{tabularx}
\end{table}
\FloatBarrier

\noindent
Test keys for Table~\ref{tab:nfr-trace-a}:
LF1 = NF.LF.1, LF2 = NF.LF.2, US1 = NF.US.1,
US2 = NF.US.2, PF1 = NF.PF.1, PF2 = NF.PF.2.

\begin{table}[H]
\centering
\small
\caption{Non-Functional Requirements Traceability Matrix Part 2}
\label{tab:nfr-trace-b}
\begin{tabularx}{\textwidth}{|c|*{6}{>{\centering\arraybackslash}X|}}
\hline
Req ID & PF3 & OP1 & OP2 & SEC1 & SEC2 & COM1 \\
\hline
SAF.R.1 & $\times$ & & & & $\times$ & \\
\hline
SAF.R.2 & $\times$ & & & & & \\
\hline
SOE.R.1 & $\times$ & & & & & \\
\hline
SOE.R.2 & $\times$ & & & & & \\
\hline
LON.R.1 & $\times$ & & & & & \\
\hline
LON.R.2 & $\times$ & & & & & \\
\hline
EPE.R.1 & & $\times$ & & & & \\
\hline
EPE.R.2 & & $\times$ & & & & \\
\hline
EPE.R.3 & & $\times$ & & & & \\
\hline
EPE.R.4 & & $\times$ & & & & \\
\hline
WER.R.1 & & $\times$ & & & & \\
\hline
WER.R.2 & & $\times$ & & & & \\
\hline
IAS.R.1 & & & $\times$ & & & \\
\hline
IAS.R.2 & & & $\times$ & & & \\
\hline
IAS.R.3 & & & $\times$ & & & \\
\hline
IAS.R.4 & & & $\times$ & & & \\
\hline
PRD.R.1 & & & $\times$ & & & \\
\hline
PRD.R.2 & & & $\times$ & & & \\
\hline
PRD.R.3 & & & $\times$ & & & \\
\hline
REL.R.1 & & & $\times$ & & & \\
\hline
REL.R.2 & & & $\times$ & & & \\
\hline
ACS-01 & & & & $\times$ & & \\
\hline
ACS-02 & & & & $\times$ & $\times$ & \\
\hline
INT-01 & & & & $\times$ & & \\
\hline
PRIV-01 & & & & $\times$ & & \\
\hline
IMM-01 & & & & $\times$ & & \\
\hline
IMM-02 & & & & $\times$ & & \\
\hline
LGL-01 & & & & & & $\times$ \\
\hline
LGL-02 & & & & & & $\times$ \\
\hline
STDCOMP-01 & & & & & & $\times$ \\
\hline
STDCOMP-02 & & & & & & $\times$ \\
\hline
\end{tabularx}
\end{table}
\FloatBarrier

\noindent
Test keys for Table~\ref{tab:nfr-trace-b}:
PF3 = NF.PF.3, OP1 = NF.OP.1, OP2 = NF.OP.2,
SEC1 = NF.SEC.1, SEC2 = NF.SEC.2, COM1 = NF.COM.1.


\section{Unit Test Description}

This section describes the planned unit tests for Proxi after the MIS
was completed. The goal of these tests is to check important module
logic before moving to integration and system testing.

Our general testing approach is simple. For each selected module, we
test the normal case first, then important edge cases and error cases.
Most of these tests will be automated. For modules that depend on
outside services or tools, mocks will be used instead of the real
service.

To keep the unit test section readable, each planned test is given a
short unit-test ID for traceability and a descriptive test name for
implementation.

\subsection{Unit Testing Scope}

The main modules in scope for direct unit testing are BH-Input,
BH-NLU, BH-Plan, BH-Safety, BH-Feedback, and BH-UI.

These modules were chosen because they contain important logic, are
easy to test in isolation, and have clear access programs in the
MIS.

The following are outside direct unit test scope: external speech
services, external MCP tools, browser, email, calendar, Notion, and
operating-system behaviour. These will be verified through mocks,
integration tests, and system tests instead.

Some support modules, such as SD-Types, SD-Store, SD-AIClient,
SD-ToolRegistry, and SD-Log, are lower priority for direct unit
testing in this document. They are either simple support modules or
are tested indirectly through higher-priority modules.

\subsection{Tests for Functional Requirements}

Most unit verification will be done using automated tests. The test
cases below are grouped by module and use short unit-test IDs so
they can be traced later in the report.

\subsubsection{Tests for BH-Input}

BH-Input is unit tested because it handles voice and text input,
state changes, and input retrieval.

\begin{enumerate}

\item \textbf{UT.INPUT.1 --
\texttt{test\_bh\_input\_init\_sets\_idle\_state}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Module not initialized.

\textbf{Input/Condition:} Call \texttt{initInput()}.

\textbf{Output/Result:} State becomes Idle, mode becomes TextOnly, and stored
text is empty.

\textbf{How test will be performed:} An automated unit test will call
\texttt{initInput()} and check the returned or stored state.

\item \textbf{UT.INPUT.2 --
\texttt{test\_bh\_input\_start\_capture\_from\_idle}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Module initialized and idle.

\textbf{Input/Condition:} Call \texttt{startCapture(Mixed)}.

\textbf{Output/Result:} State becomes Listening and mode becomes Mixed.

\textbf{How test will be performed:} An automated unit test will start capture
and check the new state.

\item \textbf{UT.INPUT.3 --
\texttt{test\_bh\_input\_duplicate\_start\_raises\_error}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Module already listening.

\textbf{Input/Condition:} Call \texttt{startCapture(VoiceOnly)} again.

\textbf{Output/Result:} Exception \texttt{AlreadyCapturing} is raised.

\textbf{How test will be performed:} An automated unit test will start capture
once and then call it again.

\item \textbf{UT.INPUT.4 --
\texttt{test\_bh\_input\_stop\_capture\_returns\_idle}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Module listening or processing.

\textbf{Input/Condition:} Call \texttt{stopCapture()}.

\textbf{Output/Result:} State returns to Idle.

\textbf{How test will be performed:} An automated unit test will start capture,
stop it, and verify the resulting state.

\item \textbf{UT.INPUT.5 --
\texttt{test\_bh\_input\_get\_last\_text\_raises\_when\_empty}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Module initialized with no stored text.

\textbf{Input/Condition:} Call \texttt{getLastText()}.

\textbf{Output/Result:} Exception \texttt{NoInputAvailable} is raised.

\textbf{How test will be performed:} An automated unit test will initialize the
module and request the last text right away.

\end{enumerate}

\subsubsection{Tests for BH-NLU}

BH-NLU is unit tested because it converts input text into intents and
parameters, and its behaviour is mostly deterministic.

\begin{enumerate}

\item \textbf{UT.NLU.1 --
\texttt{test\_bh\_nlu\_parse\_email\_command}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Parser available.

\textbf{Input/Condition:} Call \texttt{parseText("Draft an email to John about
tomorrow's meeting")}.

\textbf{Output/Result:} Returned intent matches draft-email and includes useful
parameters.

\textbf{How test will be performed:} An automated unit test will compare the
returned intent type and fields to the expected values.

\item \textbf{UT.NLU.2 --
\texttt{test\_bh\_nlu\_parse\_calendar\_command}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Parser available.

\textbf{Input/Condition:} Call \texttt{parseText("Create a calendar event for
Friday at 2 PM called Team Sync")}.

\textbf{Output/Result:} Returned intent matches create-calendar-event and
includes time and title information.

\textbf{How test will be performed:} An automated unit test will verify the
returned type and parsed fields.

\item \textbf{UT.NLU.3 --
\texttt{test\_bh\_nlu\_unsupported\_command\_raises\_parse\_error}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Parser available.

\textbf{Input/Condition:} Call \texttt{parseText("Paint my room blue")}.

\textbf{Output/Result:} Exception \texttt{ParseError} is raised.

\textbf{How test will be performed:} An automated unit test will give an
unsupported command and check the exception.

\end{enumerate}

\subsubsection{Tests for BH-Plan}

BH-Plan is unit tested because it creates plans from intents and
controls execution behaviour. External tools are mocked in these
tests.

\begin{enumerate}

\item \textbf{UT.PLAN.1 --
\texttt{test\_bh\_plan\_init\_sets\_default\_state}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Module not initialized.

\textbf{Input/Condition:} Call \texttt{initPlan()}.

\textbf{Output/Result:} Current plan is null and last status is Pending.

\textbf{How test will be performed:} An automated unit test will initialize the
module and check the stored values.

\item \textbf{UT.PLAN.2 --
\texttt{test\_bh\_plan\_create\_plan\_for\_supported\_intent}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Module initialized with a mocked valid tool registry.

\textbf{Input/Condition:} Call \texttt{planAction(i)} for a supported intent.

\textbf{Output/Result:} A plan is created with the expected tool and parameters.

\textbf{How test will be performed:} An automated unit test will mock the tool
registry and compare the returned plan.

\item \textbf{UT.PLAN.3 --
\texttt{test\_bh\_plan\_missing\_tool\_raises\_error}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Module initialized with no matching tool.

\textbf{Input/Condition:} Call \texttt{planAction(i)} for an unsupported tool
type.

\textbf{Output/Result:} Exception \texttt{NoToolFound} is raised.

\textbf{How test will be performed:} An automated unit test will use a mocked
registry with no valid match.

\item \textbf{UT.PLAN.4 --
\texttt{test\_bh\_plan\_execute\_plan\_updates\_status}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Module initialized with a valid mocked plan.

\textbf{Input/Condition:} Call \texttt{executePlan(p)}.

\textbf{Output/Result:} Status becomes Success or Failed based on the mocked
tool result.

\textbf{How test will be performed:} An automated unit test will mock tool
results and check the final status.

\item \textbf{UT.PLAN.5 --
\texttt{test\_bh\_plan\_cancel\_without\_pending\_plan\_fails}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Module initialized with no pending plan.

\textbf{Input/Condition:} Call \texttt{cancelPlan()}.

\textbf{Output/Result:} Exception \texttt{NoPendingPlan} is raised.

\textbf{How test will be performed:} An automated unit test will call
\texttt{cancelPlan()} after initialization and verify the exception.

\end{enumerate}

\subsubsection{Tests for BH-Safety}

BH-Safety is unit tested because it contains important decision rules
for risky actions and confirmations.

\begin{enumerate}

\item \textbf{UT.SAFE.1 --
\texttt{test\_bh\_safety\_low\_risk\_action\_is\_allowed}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Safety module available.

\textbf{Input/Condition:} Pass a low-risk action to the safety policy
functions.

\textbf{Output/Result:} The action is automatically allowed.

\textbf{How test will be performed:} An automated unit test will create a mock
low-risk action and verify the result.

\item \textbf{UT.SAFE.2 --
\texttt{test\_bh\_safety\_high\_irreversible\_action\_is\_blocked}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Safety module available.

\textbf{Input/Condition:} Pass a high-risk irreversible action to the safety
policy functions.

\textbf{Output/Result:} The action is blocked.

\textbf{How test will be performed:} An automated unit test will create a mock
high-risk action and verify the result.

\item \textbf{UT.SAFE.3 --
\texttt{test\_bh\_safety\_medium\_risk\_asks\_for\_confirmation}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Safety module available with mocked user response.

\textbf{Input/Condition:} Pass a medium-risk action to the confirmation path.

\textbf{Output/Result:} The action requires user confirmation and follows the
mocked yes or no response.

\textbf{How test will be performed:} An automated unit test will mock the user
response and verify the returned decision.

\item \textbf{UT.SAFE.4 --
\texttt{test\_bh\_safety\_confirmation\_timeout\_raises\_error}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Safety module available with no user response.

\textbf{Input/Condition:} Pass an action that needs confirmation to the
confirmation path.

\textbf{Output/Result:} The module raises the expected timeout error.

\textbf{How test will be performed:} An automated unit test will simulate no
response and verify the timeout behaviour.

\end{enumerate}

\subsubsection{Tests for BH-Feedback}

BH-Feedback is unit tested because it controls queue behaviour,
delivery state, and cancellation logic.

\begin{enumerate}

\item \textbf{UT.FEED.1 --
\texttt{test\_bh\_feedback\_init\_sets\_idle\_and\_empty\_queue}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Module not initialized.

\textbf{Input/Condition:} Call \texttt{initFeedback()}.

\textbf{Output/Result:} Queue is empty and status is Idle.

\textbf{How test will be performed:} An automated unit test will initialize the
module and check the queue and status.

\item \textbf{UT.FEED.2 --
\texttt{test\_bh\_feedback\_queue\_message\_appends\_successfully}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Module initialized.

\textbf{Input/Condition:} Call \texttt{queueMessage("Ready", Both)}.

\textbf{Output/Result:} The message is added to the queue.

\textbf{How test will be performed:} An automated unit test will queue one
message and check the queue size.

\item \textbf{UT.FEED.3 --
\texttt{test\_bh\_feedback\_speak\_now\_updates\_completed\_state}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Module initialized with mocked output channels.

\textbf{Input/Condition:} Call \texttt{speakNow("Done", Both)}.

\textbf{Output/Result:} The final status becomes Completed on success.

\textbf{How test will be performed:} An automated unit test will mock the
output channels and check the final status.

\item \textbf{UT.FEED.4 --
\texttt{test\_bh\_feedback\_tts\_failure\_is\_handled}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Module initialized with a failing mocked TTS path.

\textbf{Input/Condition:} Call \texttt{speakNow("Done", VoiceOnly)}.

\textbf{Output/Result:} The expected failure path or exception is triggered.

\textbf{How test will be performed:} An automated unit test will mock TTS
failure and verify the result.

\item \textbf{UT.FEED.5 --
\texttt{test\_bh\_feedback\_cancel\_clears\_queue}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} Module initialized with queued messages.

\textbf{Input/Condition:} Call \texttt{cancelAll()}.

\textbf{Output/Result:} Queue is empty and status returns to Idle.

\textbf{How test will be performed:} An automated unit test will queue
messages, cancel them, and check the final state.

\end{enumerate}

\subsubsection{Tests for BH-UI}

BH-UI is unit tested for state changes and message handling. Visual
quality itself is checked mainly by system tests.

\begin{enumerate}

\item \textbf{UT.UI.1 --
\texttt{test\_bh\_ui\_init\_sets\_idle\_state}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} UI module not initialized.

\textbf{Input/Condition:} Call \texttt{initUI()}.

\textbf{Output/Result:} State becomes Idle and last message is empty.

\textbf{How test will be performed:} An automated unit test will initialize the
module and check the state.

\item \textbf{UT.UI.2 --
\texttt{test\_bh\_ui\_update\_view\_changes\_ui\_state}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} UI module initialized.

\textbf{Input/Condition:} Call \texttt{updateView(Listening)}.

\textbf{Output/Result:} UI state changes to Listening.

\textbf{How test will be performed:} An automated unit test will call
\texttt{updateView()} and verify the new state.

\item \textbf{UT.UI.3 --
\texttt{test\_bh\_ui\_show\_message\_stores\_message}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} UI module initialized.

\textbf{Input/Condition:} Call \texttt{showMessage("Draft created")}.

\textbf{Output/Result:} The stored message is updated and the UI state becomes
Displaying.

\textbf{How test will be performed:} An automated unit test will call
\texttt{showMessage()} and check the resulting state.

\item \textbf{UT.UI.4 --
\texttt{test\_bh\_ui\_prompt\_user\_returns\_response}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} UI module initialized with mocked user response.

\textbf{Input/Condition:} Call \texttt{promptUser("Send this email?")}.

\textbf{Output/Result:} The prompt path returns the expected user response.

\textbf{How test will be performed:} An automated unit test will mock the user
response and verify the returned value.

\item \textbf{UT.UI.5 --
\texttt{test\_bh\_ui\_clear\_screen\_resets\_display}}

\textbf{Type:} Functional, Dynamic, Automatic

\textbf{Initial State:} UI module initialized with a shown message.

\textbf{Input/Condition:} Call \texttt{clearScreen()}.

\textbf{Output/Result:} State returns to Idle and the message is cleared.

\textbf{How test will be performed:} An automated unit test will show a
message, clear the screen, and verify the final state.

\end{enumerate}

\subsection{Tests for Non-Functional Requirements}

Most non-functional requirements are checked better by integration and
system testing. Only a few simple unit-level checks are included here.

\subsubsection{Tests for BH-Feedback}

\begin{enumerate}

\item \textbf{UT.NF.FEED.1 --
\texttt{test\_bh\_feedback\_cancel\_leaves\_no\_queued\_messages}}

\textbf{Type:} Non-Functional, Dynamic, Automatic

\textbf{Initial State:} Feedback module initialized.

\textbf{Input/Condition:} Queue a few messages and then call
\texttt{cancelAll()}.

\textbf{Output/Result:} Queue becomes empty and status returns to Idle.

\textbf{How test will be performed:} An automated unit test will queue
messages, cancel them, and check the final state.

\end{enumerate}

\subsubsection{Tests for BH-Safety}

\begin{enumerate}

\item \textbf{UT.NF.SAFE.1 --
\texttt{test\_bh\_safety\_high\_risk\_action\_is\_never\_auto\_approved}}

\textbf{Type:} Non-Functional, Dynamic, Automatic

\textbf{Initial State:} Safety module available.

\textbf{Input/Condition:} Pass a high-risk irreversible action to the safety
policy functions.

\textbf{Output/Result:} The action is blocked or requires confirmation, but it
is never auto-approved.

\textbf{How test will be performed:} An automated unit test will create a mock
high-risk action and verify the result.

\end{enumerate}

\subsection{Traceability Between Test Cases and Modules}

Tables~\ref{tab:unit-mod-func} and \ref{tab:unit-mod-nf} map the
planned unit tests to the main modules selected for direct unit
verification.

Modules not shown in these tables were still considered during planning,
but they are verified mainly through integration tests, system tests, or
inspection rather than direct detailed unit tests.

\noindent

\begin{table}[htbp]
\centering
\small
\caption{Functional Unit Test Traceability Matrix}
\label{tab:unit-mod-func}
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
Test ID & IN & NLU & PLN & SAF & FDB & UI \\
\hline
UT.INPUT.1 & $\times$ & & & & & \\
\hline
UT.INPUT.2 & $\times$ & & & & & \\
\hline
UT.INPUT.3 & $\times$ & & & & & \\
\hline
UT.INPUT.4 & $\times$ & & & & & \\
\hline
UT.INPUT.5 & $\times$ & & & & & \\
\hline
UT.NLU.1 & & $\times$ & & & & \\
\hline
UT.NLU.2 & & $\times$ & & & & \\
\hline
UT.NLU.3 & & $\times$ & & & & \\
\hline
UT.PLAN.1 & & & $\times$ & & & \\
\hline
UT.PLAN.2 & & & $\times$ & & & \\
\hline
UT.PLAN.3 & & & $\times$ & & & \\
\hline
UT.PLAN.4 & & & $\times$ & & & \\
\hline
UT.PLAN.5 & & & $\times$ & & & \\
\hline
UT.SAFE.1 & & & & $\times$ & & \\
\hline
UT.SAFE.2 & & & & $\times$ & & \\
\hline
UT.SAFE.3 & & & & $\times$ & & \\
\hline
UT.SAFE.4 & & & & $\times$ & & \\
\hline
UT.FEED.1 & & & & & $\times$ & \\
\hline
UT.FEED.2 & & & & & $\times$ & \\
\hline
UT.FEED.3 & & & & & $\times$ & \\
\hline
UT.FEED.4 & & & & & $\times$ & \\
\hline
UT.FEED.5 & & & & & $\times$ & \\
\hline
UT.UI.1 & & & & & & $\times$ \\
\hline
UT.UI.2 & & & & & & $\times$ \\
\hline
UT.UI.3 & & & & & & $\times$ \\
\hline
UT.UI.4 & & & & & & $\times$ \\
\hline
UT.UI.5 & & & & & & $\times$ \\
\hline
\end{tabular}
\end{table}

\noindent
Module keys:
IN = BH-Input, NLU = BH-NLU, PLN = BH-Plan, SAF = BH-Safety,
FDB = BH-Feedback, UI = BH-UI.

\begin{table}[htbp]
\centering
\small
\caption{Non-Functional Unit Test Traceability Matrix}
\label{tab:unit-mod-nf}
\begin{tabular}{|l|c|c|}
\hline
Test ID & SAF & FDB \\
\hline
UT.NF.SAFE.1 & $\times$ & \\
\hline
UT.NF.FEED.1 & & $\times$ \\
\hline
\end{tabular}
\end{table}

\noindent
The selected modules receive direct unit testing because they contain the
main deterministic logic of Proxi. Other modules, such as BH-Session,
HH-IO, HH-Auto, SD-Store, SD-Log, SD-AIClient, and external services,
are verified more effectively through integration tests, system tests,
and inspection.

\FloatBarrier

\bibliographystyle{plainnat}

\bibliography{../../refs/References}

\newpage

\section{Appendix}

This is where you can place additional information.

\subsection{Symbolic Parameters}

The definition of the test cases will call for SYMBOLIC\_CONSTANTS.
Their values are defined in this section for easy maintenance.

\subsection{Usability Survey Questions}

The purpose of this survey is to validate that Project Proxi meets its
usability, accessibility, and satisfaction goals from the SRS. Responses
will be collected after user testing sessions to evaluate clarity,
efficiency, and inclusiveness. Each question below lists how the response
will be recorded and the intent behind it.

\vspace{0.5em}
\begin{enumerate}

\item \textbf{How easy was it to perform tasks using voice commands?}\\
Response Type: 1–5 scale (Very Hard → Very Easy).\\
Intent: Measure how intuitive and learnable the system is for new users.

\item \textbf{Were system responses clear and understandable?}\\
Response Type: 1–5 scale (Very Unclear → Very Clear).\\
Intent: Assess clarity of feedback and correctness of system output.

\item \textbf{Did the system react quickly to your commands?}\\
Response Type: 1–5 scale (Very Slow → Very Fast).\\
Intent: Validate perceived responsiveness and latency satisfaction.

\item \textbf{How intuitive did the interface feel while completing tasks?}\\
Response Type: 1–5 scale (Confusing → Very Intuitive).\\
Intent: Evaluate the overall user interface flow and predictability.

\item \textbf{Was visual or audio feedback easy to notice and understand?}\\
Response Type: 1–5 scale (Not Accessible → Highly Accessible).\\
Intent: Verify accessibility and multimodal feedback effectiveness.

\item \textbf{Did you feel confident that Proxi understood your intent?}\\
Response Type: 1–5 scale (Never → Always).\\
Intent: Measure trust in speech recognition and NLP accuracy.

\item \textbf{How satisfied are you with the overall experience?}\\
Response Type: 1–5 scale (Very Unsatisfied → Very Satisfied).\\
Intent: Determine overall satisfaction and user acceptance level.

\item \textbf{Did you encounter confusion or frustration while using Proxi?}\\
Response Type: Open text.\\
Intent: Identify specific usability or interaction issues.

\item \textbf{Would you consider using Proxi for daily tasks?}\\
Response Type: Yes / No.\\
Intent: Gauge adoption potential and long-term usability perception.

\item \textbf{Do you have any comments or suggestions for improvement?}\\
Response Type: Open text.\\
Intent: Gather qualitative feedback for future iterations.

\end{enumerate}

\newpage{}
\section*{Appendix --- Reflection}

\wss{This section is not required for CAS 741}

The information in this section will be used to evaluate the team members on the
graduate attribute of Lifelong Learning.

\input{../Reflection.tex}

\begin{enumerate}
  \item What went well while writing this deliverable? 
  \item What pain points did you experience during this deliverable, and how
    did you resolve them?
  \item What knowledge and skills will the team collectively need to acquire to
  successfully complete the verification and validation of your project?
  Examples of possible knowledge and skills include dynamic testing knowledge,
  static testing knowledge, specific tool usage, Valgrind etc.  You should look to
  identify at least one item for each team member.
  \item For each of the knowledge areas and skills identified in the previous
  question, what are at least two approaches to acquiring the knowledge or
  mastering the skill?  Of the identified approaches, which will each team
  member pursue, and why did they make this choice?
\end{enumerate}

\newpage
\section*{Reflection --- Amanbeer Singh Minhas}

\textbf{1. What went well while writing this deliverable?}  
For this deliverable, I worked mainly on Section 3 (Plan) and Section 6.2
(Usability Survey Questions). These sections went well because they helped
connect the technical and human sides of our project. In Section 3, I focused
on creating a clear roadmap for verification that was realistic for our team.
It felt good to see how each part linked to the SRS and our earlier work.
Section 6.2 was also rewarding because it allowed me to design usability
questions that measure user experience in a meaningful way.

\noindent\textbf{2. What pain points did you experience during this deliverable, and how
did you resolve them?}  
The main challenge was figuring out how much detail to include in each
section. At first, some parts of our plan were too general, while others were
too detailed. Finding the right balance took a few rounds of review and
feedback. Another difficulty was maintaining consistency in tone and wording
across sections written by different team members. I helped fix this by
revising and merging ideas so the final version felt smooth and unified.

\noindent\textbf{3. What knowledge and skills will the team collectively need to acquire
to successfully complete the verification and validation of your project?}  
As a team, we realized we need stronger testing and validation skills. I plan
to improve my understanding of automated documentation, coverage metrics, and
survey analysis. Savinay aims to deepen his knowledge of integration testing.
Gourob wants to explore performance and stress testing for our AI modules, and
Ajay is focusing on automated UI and accessibility verification.

\noindent\textbf{4. For each of the knowledge areas and skills identified in the
previous question, what are at least two approaches to acquiring the knowledge
or mastering the skill? Of the identified approaches, which will each team
member pursue, and why did they make this choice?}  
To build the skills we identified, our team plans to rely on both formal and
self-directed learning. We will start by reviewing course material from
SFWRENG 3S03, which covered testing concepts such as unit testing, coverage,
and static analysis. This will help refresh the theoretical foundation before
moving into practical work. We also plan to read online documentation and
tutorials on dynamic testing and usability validation to better understand
industry practices. Each member will then apply this knowledge directly to
our project tasks for example, by creating small prototype tests or running
sample validation sessions. This approach keeps learning active and helps us
improve through real application instead of only theory.

\section*{Reflection --- Ajay Singh Grewal}

\textbf{1. What went well while writing this deliverable?}  
For this deliverable, I worked mainly on section 4.2 to figure out the tests
for non-functional requirements. This section went pretty good for me because
it allowed me to think critically about how to measure different aspects
for our software and how to make sure it essentially meets the needs of our users.

\noindent\textbf{2. What pain points did you experience during this deliverable, and how
did you resolve them?}  
The main challenge I had faced during this deliverable was making sure that the 
test cases for the non-functional requirements made sense and were realistic to 
do. To properly do this, I had to really think about what our software was going
to be used for and how we could truly measure the success of these 
non-functional requirements.

\noindent\textbf{3. What knowledge and skills will the team collectively need to acquire
to successfully complete the verification and validation of your project?}  
The knowledge and skills that our team will need in order to ensure success
in the verification and validation of our project include dynamic testing
knowledge, static testing knowledge, and certain tool usage. I hope to improve 
my knowledge in various testing methods that can help verify and validate our 
project.  

\noindent\textbf{4. For each of the knowledge areas and skills identified in the
previous question, what are at least two approaches to acquiring the knowledge
or mastering the skill? Of the identified approaches, which will each team
member pursue, and why did they make this choice?}  
For each of the knowledge areas and skills we identified, our team plans to 
use a combination of formal and self-directed learning. We can start by reviewing 
course material and by reading online articles and tutorials on relevant topics.
Each member will then apply this learned knowledge directly into the successful
creation of our project. We can also do small prototype tests or run sample 
validation sessions to help us learn better.

\section*{Reflection --- Gourob Podder}

\textbf{1. What went well while writing this deliverable?}  

Writing this deliverable went smoothly once I established a clear mapping
 between each functional requirement and its corresponding tests. The structure 
 of the SRS helped guide our testing logic, and I was able to design specific, 
 measurable, and realistic test cases for all major system components from input 
 handling to agent-based task execution. Collaboratively, we divided responsibilities 
 efficiently, which allowed us to maintain a consistent level of technical depth and 
 clarity throughout the V\&V plan.

\noindent\textbf{2. What pain points did you experience during this deliverable, and how did you resolve them?}  

One major challenge we faced was time management. Our group had to apply for an MSAF 
(McMaster Student Absence Form) to obtain academic relief for a late submission due 
to unexpected health issues amongst our group members. Getting approval 
for the MSAF was a bit of a hassle --- it required communication with the professor and the 
relevant university department. This delay temporarily disrupted our workflow and 
added stress to the deliverable timeline. We resolved it by setting up a stricter internal 
schedule after the approval to get the work completed efficiently.  

\noindent\textbf{3. What knowledge and skills will the team collectively need to acquire to successfully complete the verification and validation of your project?}  
We had to learn a lot on how testing and verification worked for black boxes
like LLMs:  
\begin{itemize}
    \item Testing and evaluation of AI/NLP models (e.g., measuring intent classification 
    accuracy and ASR performance).  
    \item Usability testing with diverse user groups, particularly those with 
    accessibility needs.  
\end{itemize}

\noindent\textbf{4. For each of the knowledge areas and skills identified in the previous question, what are at least two approaches to acquiring the knowledge or mastering the skill? Of the identified approaches, which will each team member pursue, and why did they make this choice?}  

\begin{itemize}
    \item \textbf{AI/NLP Testing and Evaluation:}  
    Approaches include (1) completing online courses or tutorials on NLP evaluation 
    (e.g., Coursera, Hugging Face documentation) and (2) implementing small-scale 
    evaluation scripts for our ASR and intent recognition modules. I will focus 
    on the implementation approach since I already have a strong technical 
    background and prefer hands-on experimentation with model outputs.  

    \item \textbf{Usability and Accessibility Testing:}  
    Approaches include (1) conducting supervised user testing sessions with 
    accessibility-focused participants. One of our teammates with a human--computer 
    interaction background will lead user testing, while I will focus on analyzing 
    the qualitative data collected from these sessions to guide improvements.  
\end{itemize}




\section*{Reflection --- Savinay Chhabra}

\textbf{1. What went well while writing this deliverable?}  
The team did a much better job communicating what each team member was doing 
well in advance. This made working on dependent sections a lot easier than 
previous deliverables. This prevented unnecessary back and forth between team 
members which saved significant time.

\noindent\textbf{2. What pain points did you experience during this deliverable, and how
did you resolve them?}  
The biggest challenge with this deliverable was that the entire team was absent 
for the deadline and several days before that as well. We were unclear on how to 
request academic relief which made it even more challenging. In the end, we were
able to work with the Office of the Associate Dean and the course professor to 
get an extension. All this would have been a lot simpler and easier for everyone 
if we requested academic relief well before the deadline.

\noindent\textbf{3. What knowledge and skills will the team collectively need to acquire
to successfully complete the verification and validation of your project?}  
Some basic verification and validation skills including coming up with test plans,
scenarios, user groups and correctness are required. This is important as the 
objectives we wish to validate would require comprehensive test cases which 
cover the vast majority of scenarios we would expect to see in the real world. 
For that, knowledge about Unit Testing, Integration Testing, Stability Testing 
and End to End Integration Testing would be very useful to have.

\noindent\textbf{4. For each of the knowledge areas and skills identified in the
previous question, what are at least two approaches to acquiring the knowledge
or mastering the skill? Of the identified approaches, which will each team
member pursue, and why did they make this choice?}  
A good start would be to review prior course material that taught us all of 
these concepts. SFWRENG 3S03 was a very useful course that taught about testing. 
This would help build a strong theoretical foundation. For practical learning, 
going through open source software projects and their tests (both automated and 
manual) would be very helpful. Reading their test plans and contributing to their
testing when feasible would be a great way to get some practical experience.

\end{document}